Modeling memory and taxis to analyze migrations

### 2021-07-09 text/ms.Rmd
...

cc.summary %>% subset(lambda > 40) %>% 
    ggplot(aes(kappa, FE_mean, col = factor(lambda), ymin = FE_low, ymax = FE_high)) +
    facet_grid(.~psi_x) + geom_point() + theme_few() + geom_errorbar() + 
    geom_path()

>>>>

cc.summary %>% subset(lambda > 40 & psi_x > 0) %>% 
    ggplot(aes(kappa, FE_mean, col = factor(lambda), ymin = FE_low, ymax = FE_high)) +
    facet_grid(.~psi_x) + geom_point() + theme_few() + geom_errorbar() + 
    geom_path()
